---
title: "reform original data"
author: "Thomas Van Hoey"
date: "10-10-2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readxl)
library(here)
library(tmcn)
#library(reticulate)
```


```{r}
df <- read_excel(here("originaldata",
                      "BaxterSagartOC2015-10-13.xlsx"))
df
```

# Add simplified as well

```{r}
df %>%
  rename(traditional = zi) %>%
  mutate(simplified = toTrad(traditional, rev = TRUE)) %>%
  select(traditional, simplified, everything()) -> df.simplified

df.simplified
```

# Add different pinyin options

```{r}
df.simplified %>%
  select(py) %>%
  distinct() -> pinyincol

pinyincol %>%
  mutate(pinyinnum = case_when(
    #a
    str_detect(py, "ā") ~ str_replace(py, "ā", "a1"),
    str_detect(py, "á") ~ str_replace(py, "á", "a2"),
    str_detect(py, "ǎ") ~ str_replace(py, "ǎ", "a3"),
    str_detect(py, "à") ~ str_replace(py, "à", "a4"),
    # e
    str_detect(py, "ē") ~ str_replace(py, "ē", "e1"),
    str_detect(py, "é") ~ str_replace(py, "é", "e2"),
    str_detect(py, "ě") ~ str_replace(py, "ě", "e3"),
    str_detect(py, "è") ~ str_replace(py, "è", "e4"),
    # i
    str_detect(py, "ī") ~ str_replace(py, "ī", "i1"),
    str_detect(py, "í") ~ str_replace(py, "í", "i2"),
    str_detect(py, "ǐ") ~ str_replace(py, "ǐ", "i3"),
    str_detect(py, "ì") ~ str_replace(py, "ì", "i4"),
    # o
    str_detect(py, "ō") ~ str_replace(py, "ō", "o1"),
    str_detect(py, "ó") ~ str_replace(py, "ó", "o2"),
    str_detect(py, "ǒ") ~ str_replace(py, "ǒ", "o3"),
    str_detect(py, "ò") ~ str_replace(py, "ò", "o4"),
    # u
    str_detect(py, "ū") ~ str_replace(py, "ū", "u1"),
    str_detect(py, "ú") ~ str_replace(py, "ú", "u2"),
    str_detect(py, "ǔ") ~ str_replace(py, "ǔ", "u3"),
    str_detect(py, "ù") ~ str_replace(py, "ù", "u1"),
    # ü
    #str_detect(py, "ī") ~ str_replace(py, "ī", "ü1"), #notpresent
    str_detect(py, "ǘ") ~ str_replace(py, "ǘ", "ü2"),
    str_detect(py, "ǚ") ~ str_replace(py, "ǚ", "ü3"),
    str_detect(py, "ǜ") ~ str_replace(py, "ǜ", "ü4"),
    TRUE ~ py
    )) %>%
  mutate(tonenumber = str_extract(pinyinnum, "\\d"),
         pinyinnone = str_remove(pinyinnum, "\\d")) %>%
  unite("pinyinnum", 
        pinyinnone:tonenumber,
        remove = FALSE,
        sep = "") %>%
  select(pinyintone = py,
         pinyinnum,
         pinyinnone,
         tonenumber) -> pinyinset
```

```{r}
pinyinset %>%
  left_join(df.simplified, 
            by = c("pinyintone" = "py")) -> pinyinexpanded
pinyinexpanded
```


# Middle Chinese

> ASCII-friendly Middle Chinese (MC) transcription. This is a minor modification of the notation used in Baxter (1992); for details see Baxter & Sagart (2014:9–20). For clarity, after each transcribed syllable we give the MC initial, final, and tone separately (with A, B, C, D for the traditional categories 平 píng, 上 shǎng, 去 qù, and 入 rù respectively): e.g. 處 chǔ, MC tsyhoX (tsyh- + -jo + B) ‘place’. Note that this notation is not intended as a reconstruction; rather it is intended as a convenient representation of the information on pronunciation given in Middle Chinese sources such as the Guǎngyùn 《廣韻》 and the Jīngdiǎn shìwén 《經典釋⽂文》.

So:
* MC
* initial, final, tone
  * tone = A,B,C,D = ping, shang, qu, ru
  
```{r}
# they one error here
pinyinexpanded[2013,]$...4 <- "(l- + -ok D)"
```
  

```{r}
pinyinexpanded %>%
  rename(MCparts =`...4`) %>%
  mutate(MCparts = str_replace_all(MCparts, "[()]", "")) %>%
  separate(MCparts, 
           into = c("MCinitial", "MCfinaltone"),
           sep = " \\+ ") %>%
  mutate(MCfinaltone = str_trim(MCfinaltone)) %>%
  separate(MCfinaltone,
           into = c("MCfinal", "MCtone"),
           sep = " ") %>%
  mutate(MCtone = case_when(
    MCtone == "A" ~ "ping",
    MCtone == "B" ~ "shang",
    MCtone == "C" ~ "qu",
    MCtone == "D" ~ "ru")) %>%
  select(traditional, 
         simplified, 
         everything())-> BaxterSagartExpanded
```


```{r}
BaxterSagartExpanded
```


Middle Chinese to IPA with sinopy

```{r}
BaxterSagartExpanded %>% select(MC) %>% pull() -> MCbaxter
```

```{r pythonreticulate}
library(reticulate)
use_python("/usr/local/bin/python3", required = T)
reticulate::py_config()
```

```{python}
from sinopy import baxter2ipa

#baxteripa = baxter2ipa(r.MCbaxter)

#print(baxteripa)

baxteripa = []
for baxter in r.MCbaxter:
  ipa = baxter2ipa(baxter)
  baxteripa.append(ipa)

print(baxteripa)

```

```{r}
py$baxteripa
```

