---
title: "Making Datapackage with DataPackageR"
author: "Thomas Van Hoey"
date: "1/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Steps described in:

* [](https://ropensci.org/blog/2018/09/18/datapackager/)
* [](https://github.com/ropensci/DataPackageR)

On the why:

* [](https://grasshoppermouse.github.io/2017/10/18/put-your-data-in-an-r-package/)

Other methods:

* [](https://www.erikhoward.net/how-to-create-an-r-data-package/)
* [](http://www.clayford.net/statistics/creating-an-r-data-package/)

# Set up
```{r}
library(DataPackageR)
library(here)
library(tidyverse)
library(readxl)
```

# Variables

```{r}
PATH <- here()
PACKAGENAME <- "baxteRsagaRt" #Chinese Lexical Database R
```


# Reading in the data

**SO THIS WILL BECOME THE NEW FILE REFORMED THAT I NEED TO READ IN** 

```{r}
#df <- read_excel(here("originaldata",
#                      "BaxterSagartOC2015-10-13.xlsx"))

df <- read_csv(here("originaldata",
                    "BaxterSagartreformed.csv"))
df
```

# Manipulations

```{r}

```


# Create a data package directory structure.

```{r}
datapackage_skeleton(name = PACKAGENAME,
                     path = PATH,
                     force = TRUE)
```

# Add raw data to the package.
```{r}
# NOW WITH RDS
# write our raw data to a csv 
#write.csv(x = df,file = file.path(PATH, "chideod.csv"), row.names = FALSE)

# write raw data to rds
#write_csv(df, file.path(PATH, "cld.csv"))

# this works because we called datapackage_skeleton() first.
#use_raw_dataset(file.path(PATH, "cld.csv"))

# Just try the rda file?
#use_raw_dataset(file.path(PATH, "cld_extended.rda"))
use_raw_dataset(file.path(here("originaldata",
                    "BaxterSagartreformed.csv")))
```


# Add a data processing script.

```{r}
use_processing_script(file = "baxter_sagart.Rmd",
                      author = "Thomas Van Hoey",
                      title = "Process Baxter and Sagart's list into data package")
```


# Edit your processing script (the Rmd file)


```
---
title: Process Baxter Sagart reformed file into datapackage
author: Thomas Van Hoey
date:  8 December, 2019
output_format: html_document
---

```{r}
baxtersagart <- df
```

```

# Let DataPackageR know about the data objects to store in the package.

```{r}
use_data_object("baxtersagart")
```

# Build the package (for the first time).

```{r}
options("DataPackageR_interact" = FALSE)
package_build(packageName = file.path(PATH, "baxteRsagaRt"),
              install = FALSE)
```

# Next edit the data set documentation.
File can be found under `data-raw`, the `documentation.R` file

>This is standard roxygen markup. You can use roxygen or markdown style comments. You should 
* describe your data set, 
* where it comes from, 
* the columns of the data (if applicable), and 
* any other information that can help a user make good use of and understand the data set. 
We’ll fill this in and save the resulting file.

```

#' baxteRsagaRt
#' A data package for baxteRsagaRt.
#' @docType package
#' @aliases baxteRsagaRt-package
#' @title Baxter Sagart -- list of Middle Chinese and Old Chinese reconstructions
#' @name baxteRsagaRt
#' @description This package contains the list of almost 5000  Middle Chinese and Old Chinese reconstructed phonologies.
#' @details Use \code{data(package='baxteRsagaRt')$results[, 3]} to see a list of available data sets in this data package
#'     and/or DataPackageR::load_all
#' _datasets() to load them.
#' @seealso
#' \link{baxtersagart}
NULL



#' Detailed description of the data
#' @name baxtersagart
#' @docType data
#' @title Baxter Sagart -- list of Middle Chinese and Old Chinese reconstructions
#' @format a \code{spec_tbl_df} containing the following fields:
#' \describe{
#' \item{traditional}{Character in traditional}
#' \item{simplified}{Character in simplified}
#' \item{pinyintone}{Pinyin with tone}
#' \item{pinyinnum}{Pinyin with numbers}
#' \item{pinyinnone}{Pinyin without tone or number}
#' \item{tonenumber}{Tone of the character in Mandarin}
#' \item{MCbaxter}{Middle Chinese according to Baxter & Sagart}
#' \item{MCinitial}{Middle Chinese initial according to Baxter & Sagart}
#' \item{MCfinal}{Middle Chinese final according to Baxter & Sagart}
#' \item{MCtone}{Middle Chinese tone according to Baxter & Sagart}
#' \item{MCipa}{Middle Chinese according to ipa, converted with sinopy}
#' \item{OC}{Old Chinese according to Baxter & Sagart}
#' \item{gloss}{gloss of the character}
#' \item{GSR}{number in Grammata Serica Recensq}
#' \item{HYDZD}{Position in the Hanyu Da Zidian, based on Unihan database}
#' \item{rad}{Traditional Kangxi zidian dictionary radical number}
#' \item{str}{Number of additional strokes}
#' \item{Unicode}{hexadecimal code of character in UTF-16}
#' }
#' @source The data comes from http://ocbaxtersagart.lsait.lsa.umich.edu.
#' @seealso
#' \link{baxteRsagaRt}
NULL







```

Next, run `document()` in the next chunk

```{r}
# ensure we run document() from the DataPackageR namespace and not document() from roxygen or devtools.
package_path <- file.path(PATH, PACKAGENAME)
DataPackageR::document(package_path)
```

# Iterate…

## the DESCRIPTION file

```
Package: baxteRsagaRt
Title: Data package containing the Baxter and Sagart reconstructions for Middle and Old Chinese
Version: 0.1
Authors@R: c(
    person(given = "Thomas",
           family = "Van Hoey",
           role = c("cre"),
           email = "thomas_van_hoey@hotmail.com"),
    person("William H.", "Baxter", email = " wbaxter@umich.edu", role = c("aut")),
    person("Laurent", "Sagart", email = "laurent.sagart@gmail.com", role = c("aut")))
Description: This package contains the contents of the database by Baxter & Sagart
License: GNU General Public License
Encoding: UTF-8
LazyData: true
DataVersion: 1.1
Roxygen: list(markdown = TRUE)
Date: 2019-12-08
Suggests: 
    knitr,
    rmarkdown
VignetteBuilder: knitr
RoxygenNote: 7.0.0

```


```{r}
# ensure we run document() from the DataPackageR namespace and not document() from roxygen or devtools.
package_path <- file.path(PATH, PACKAGENAME)
DataPackageR::document(package_path)
```




# A final build.

```{r}
package_build(file.path(PATH, PACKAGENAME))
```

# Installing test

```{r}
library(devtools)
# because private repo so you need my authorisation token
# I deleted it because it's like a password
AUTH_TOKEN <- ""
devtools::install_github("simazhi/cld/CLD", 
                         auth_token = AUTH_TOKEN)
#remotes::install_github("simazhi/cld/CLD")
#detach(package:devtools,unload = TRUE)
#install.packages("CHIDEOD_0.8.tar.gz", type = "source")

library(CLD)

data(package = "CLD")
cld # so it worked, the data is now here
```

# Readme file
```{r}
usethis::use_readme_rmd()
```


